Pillar 2 - Topic Modeling

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
minor changes

# Setup
```{r}
load("data_pillar_2.RDATA")
```

@@

```{r}
compute_tf_idf <- function(data) data %>%
                                   count(Code, word) %>%
                                   bind_tf_idf(term = word, document = Code, n = n)

@@

```{r function make_barplot and make_WC, out.height=8, out.width=16}
plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){

@@

## Course Level
```{r tf-idf per course, out.height=8, out.width=16}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = Code) %>%
                                          group_by(facet) %>%
                                          filter(n >= 2) %>%
                                          top_n(10, tf_idf) %>%
                                          ungroup

@@

## Concentration Level
```{r tf-idf per concentration}
tdm_top <- d_overview_stem %>%
  left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
  gather(key = "key", value = Concentration,
         c("Concentration", "Concentration (additional)"),
         na.rm = T) %>%
  filter(`Calendar Year` == "2018-2019") %>%
  count(Concentration, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Concentration, n = n) %>%
  filter(n >= 5) %>%
  group_by(Concentration) %>%
  top_n(10, tf_idf) %>%
  ungroup

# Plots
make_barplot(data = tdm_top, facet = Concentration)
make_WC(data = tdm_top, facet = Concentration)
```

# LDA

## Fitting Model
```{r}
d_overview_cast <- d_overview_stem %>%
  count(Code, word, sort = T) %>%
  cast_dtm(Code,word, n)
```

```{r}
LDA_10 <- LDA(d_overview_cast, k = 10, control = list(seed = 123))
LDA_17 <- LDA(d_overview_cast, k = 17, control = list(seed = 123))
LDA_25 <- LDA(d_overview_cast, k = 25, control = list(seed = 123))
```

>>>>

# Setup
```{r load data}
load("data_pillar_2.RDATA")
```

@@

```{r compute_tf_idf}
compute_tf_idf <- function(data) data %>%
                                   count(Code, word) %>%
                                   bind_tf_idf(term = word, document = Code, n = n)

@@

```{r plot_tf_idf}
plot_tf_idf <- function(data, top = 10, n_col = 5, plot_id = NULL){

@@

## Course Level
```{r tf-idf course, out.height=8, out.width=16}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = Code) %>%
                                          group_by(facet) %>%
                                          filter(n >= 2) %>%
                                          top_n(10, tf_idf) %>%
                                          ungroup

@@

## Concentration Level

# LDA
hist
## Fitting Model
```{r}
d_overview_cast <- d_overview %>%
  count(Code, word, sort = T) %>%
  cast_dtm(Code,word, n)
```

```{r}
LDA_10 <- LDA(d_overview, k = 10, control = list(seed = 123))
LDA_17 <- LDA(d_overview, k = 17, control = list(seed = 123))
LDA_25 <- LDA(d_overview, k = 25, control = list(seed = 123))
```
